\documentclass[10pt,letterpaper]{article}

\include{structure}

\begin{document} 


\maintitle{Congbin Guo}{July, 1979}

\noindent\href{mailto:guocongbin@gmail.com}{guocongbin@gmail.com}/\href{mailto:cguo@vmware.com}{cguo@vmare.com}\bull
\textsmaller{+}1 (650) 387-8025\bull Member of Technical Staff, VMware

\spacedhrule{0.9em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SUMMARY SECTION
%----------------------------------------------------------------------------------------

\roottitle{Professional Experience} % Top level section

\headedsection
{VMware, Member of Technical Staff}
{\textsc{Palo Alto, CA USA}} {
\headedsubsection 
{SCM infrastructure development} {Sept. 2013 -- present}
{
    \begin{itemize}
        \item VMware \href{http://bmps.eng.vmware.com}{BMPS} \& Automerge
            enhancement (home-grown branch policy management and automatic
            merge tools)
            \begin{itemize}
                \item Implement new BMPS feature of bulk editing multiple
                    branches in one transaction.
                \item Fix bugs of BMPS and Automerge.
            \end{itemize}
        \item Git infrastructure enhancement
            \begin{itemize}
                \item Implement branch policy management and Automerge features
                    for Git.
                \item Implement backend of a 
                    \href{http://git.eng.vmware.com}{web UI for browsing Git
                    repositories and creating pull requests}.
                \item Implement framework of Git repositories mirroring from
                    Git, Mercurial, Subversion, or CVS upstream.
                \item Implement tools for Git server health check, garbage
                    collection, etc.
            \end{itemize}

    \end{itemize}
}
}

\headedsection
{VMware, Member of Technical Staff}
{\textsc{Beijing, China}}{

\headedsubsection % Job title entry for the current employer
{SCM infrastructure development} {Apr. 2011 -- Sept. 2013}
{
    \begin{itemize}
        \item Perforce fail-over process automation
            \begin{itemize}
                \item Create tool in Python (\~{}2KLOC) to automate the
                    process.
                    The tool saves results of every step, so it can continue
                    the remain steps from the failed step of last running.
                    It is one of the most important tools for VMware SCM team.

                \item Implement web API for Perforce instances management site
                    to support the Perforce fail-over tool.

                \item Improve the Puppet configuration of Perforce to simplify
                    the process.
            \end{itemize}
        \item Other Perforce tools and infrastructure development
            \begin{itemize}
                \item Create tool to rebuild Perforce database.
                    It is another most important tool for VMware SCM team. 

                \item Create tools to check Perforce missing versioned files,
                    monitor extraneous files on perforce hosts, check file type
                    changes in Perforce submit, etc.

                \item Improve the web site for Perforce instances management
                    and account management.
            \end{itemize}
        \item Git infrastructure setup and development
            \begin{itemize}
                \item Setup and customize gitolite (Git access layer tool) on
                    VMware production Git server.
                    
                \item Implement automatic Git accounts provision tool for
                    full-time employees and contractors.

                \item Consolidate VMware internal version of git-p4 and fix
                    bugs.
                \item Maintain VMware legacy gitorious server.
            \end{itemize}
        \item Other build infrastructure maintenance and support
            \begin{itemize}
                \item Create Puppet modules to configure the primary/hot-spare
                    instances of Perforce instances management web site, VMware
                    internal maven repository and production Git server in
                    local and remote data centers.
                \item Maintain VMware production maven repository and
                    Subversion server.
            \end{itemize}

    \end{itemize}
}
\headedsubsection % Job title entry for the current employer
{VMware ESX/Workstation build enhancement} {Aug. 2010 -- Apr. 2011}
{
    \begin{itemize}
        \item VMware ESX build enhancement
            \begin{itemize}
                \item Fix legacy bugs of SCons/ESX build.
                \item Optimize the disk space consumed in ESX build process.
            \end{itemize}
        \item VMware Workstation build enhancement
            \begin{itemize}
                \item Improve the performance of Make and Ant build.
                \item Add new features to facilitate developers.
            \end{itemize}
    \end{itemize}
}
}



%------------------------------------------------

\headedsection 
{IBM China System \& Technology Lab., Staff Software Engineer}
{\textsc{Beijing, China}} {

\headedsubsection % Job title entry for the current employer
{Tech. lead of IBM Systems Director\texttrademark Development on IBM Power
Systems}
{Oct. 2008 -- Aug. 2010}
{
    \begin{itemize}
        \item Lead team to work on parts of IBM Systems Director\texttrademark
            (hereafter Director) update manager.
        \item Lead team to work on IBM Common Director Appliance for
            exploiters.
    \end{itemize}
}
}

\headedsection 
{IBM China System \& Technology Lab., Software Engineer}
{\textsc{Beijing, China}} {

\headedsubsection % Job title entry for the current employer
{Tech. lead of IBM Systems Director\texttrademark Development on IBM Power
systems}
{Apr. 2006 -- Aug. 2008}
{
    \begin{itemize}
        \item CIM (Common Information Modeling) and Director development on IBM Power systems.
        \begin{itemize}
            \item Enable Director on IBM Power systems.
            \item Develop CIM providers on IBM AIX53.
        \end{itemize}
        \item Tech. lead of CIM development on IBM Power systems.
        \begin{itemize}
            \item Lead the CIM provider (instance/indication/metric)
                development on IBM Power systems.
            \item Lead the Director Server extension of IBM AIX hardware
                resource monitoring.
            \item Continuously integrate kinds of tools (static analysis,
                memory leak check and code coverage measurement) with the team
                development and unit test process.
            \item Build China team image and gain extra team growth
                opportunities.
        \end{itemize}
    \end{itemize}

}
}

\spacedhrule{-0.2em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\roottitle{Education} % Top level section

\headedsection
{Beihang University}
{\textsc{Beijing, China}} {
\headedsubsection {Master degree in Computer Science \& Technology}
    {Sept. 2003 -- Apr. 2006} {}
\headedsubsection {Bachelor degree in Automation} {Sept. 1998 -- Jun. 2002} {}
}

\spacedhrule{0.5em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	SKILLS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Skills} % Top level section
{
    \bodytext{
    \begin{itemize}
        \item Strong in Python/django, C/C++, shell script, Puppet programming

        \item Strong in SCM (Perforce, Git, etc.), build (SCons, makefile,
            etc.) and packaging (RPM)

        \item Strong in Linux/IBM AIX system administration

        \item Strong in Software Engineering, Agile, Unit Testing and Test
            Driven Development

        \item Knowledgeable in VMware virtualization and Linux kernel-based
            virtualization

        \item Knowledgeable in Java, Perl, Ruby programming, eclipse plug-in
            development

        \item Knowledgeable of cloud computing, IBM Power Systems, security,
            storage and system management in Data Center

        \item Good soft skill in presentation and communication
    \end{itemize}
}}


%------------------------------------------------

\spacedhrule{1.6em}{-0.4em} % Horizontal rule - the first bracket is whitespace before and the second is after

%----------------------------------------------------------------------------------------
%	INTERESTS SECTION
%----------------------------------------------------------------------------------------

\roottitle{Awards, Certifications \& Publications} 

\headedsubsection
{Bidirectional Git Objects Transferring by Subdirectories Specified}
{2015 \textsc{VMware vRADIO}}
{\bodytext{\url{https://radio.eng.vmware.com/2015/events/1155}}}

\headedsubsection
{Monitor hardware environment based on IBM Systems Director 6.1 (Chinese)}
{2009 \textsc{IBM Developerworks}}
{\bodytext{\url{http://www.ibm.com/developerworks/cn/aix/tutorials/0905\_daill\_system/}}}

\headedsubsection
{The introduction and comparison of file transfer tools on Linux (Chinese)}
{2009 \textsc{IBM Developerworks}}
{\bodytext{\url{http://www.ibm.com/developerworks/cn/linux/l-cn-filetransfer/}}}

\headedsubsection
{A Framework that Simplifies the Complexity and Increase Manageability
of Stub Functions \\
in C development}
{2009 \textsc{Published disclosure}}
{\bodytext{\url{http://ip.com/IPCOM/000182356}}}

\headedsubsection
{Memory Management in CMPI and the Implementation in Open Pegasus}
{2008 \textsc{IBM Developerworks}}
{\bodytext{\url{http://www.ibm.com/developerworks/cn/linux/l-cn-opmem/}}}

\headedsubsection
{Script-Driven Testing Tool for CIM Providers}
{2008 \textsc{IBM Alphaworks}}
{\bodytext{\url{http://www.alphaworks.ibm.com/tech/script4cim}}}

\headedsubsection
{IBM eServer Certified Specialist -- AIX Basic Operation} {2007}{}

\headedsubsection
{IBM CSTL Bravo Award}{2007, 2008}{}
\end{document}

